TGI-spinal-power

### 2022-04-28 analysis/tgispine_lme_power.Rmd
creating more complex models for analysis

df_phs <- read.csv(file.choose())
```

@@

# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
model.cold <- glmer(VAScold ~ manipulation + (1|ID), family = 'poisson', data = df_phs)

```

>>>>

df_phs <- read.csv(file.choose())

# need to recode levels for cold_probe to reduce number of levels from 4 to 2
df_phs$cold_location[df_phs$cold_probe == 'distal'] <- 'dist_rostr' 
df_phs$cold_location[df_phs$cold_probe == 'rostral'] <- 'dist_rostr'
df_phs$cold_location[df_phs$cold_probe == 'proximal'] <- 'prox_caud'
df_phs$cold_location[df_phs$cold_probe == 'caudal'] <- 'prox_caud'
df_phs$cold_location <- as.factor(df_phs$cold_location)
```

@@

# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
model.cold <- lmer(VAScold ~ manipulation + (1+manipulation|ID), data = df_phs)
summary(model.cold)
```
# View the coefficients for each person (should vary, due to random slope model)
```{r}
coef(model.cold)
```

Now make a second, more complicated model where cold ratings are regressed by both manipulation and dermatome position (condition)
```{r}
model.cold2 <- lmer(VAScold ~ manipulation + condition + (1+manipulation|ID), 
                    data = df_phs)
summary(model.cold2)
```

Finally a third model where all predictors are added - manipulation, condition and cold location
Still just on cold ratings
```{r}
model.cold3 <- lmer(VAScold ~ manipulation + condition + cold_location +
                      (1+manipulation|ID), 
                    data = df_phs)
summary(model.cold3)
```
